\section{Test Infrastructure}
\label{section-test-infrastructure}

This chapter describes the infrastructure required to execute automated and manual tests across the Escape Doom platform. A consistent and reliable test environment is critical for maintaining test quality and enabling reproducible results across services.

\subsection*{Test Environment}

The system is built on a containerized microservice architecture. Therefore, all test environments replicate production-like conditions using:

\begin{itemize}
    \item \textbf{Docker Compose / Kubernetes (Minikube):} Local environments replicate service orchestration, routing, and scaling behavior.
    \item \textbf{TestContainers:} Used in integration and system tests to spin up real dependencies like PostgreSQL and Redis on-demand.
    \item \textbf{Flyway:} Ensures consistent database migrations across test environments for schema alignment.
\end{itemize}

\subsection*{Test Data}

\begin{itemize}
    \item \textbf{Static test data:} Predefined users, sessions, and escape rooms for repeatable scenarios.
    \item \textbf{Dynamic test data:} Generated on the fly using factories in tests for coverage of edge cases.
    \item \textbf{Schema migration tools:} Flyway migrations are applied automatically to ensure a valid schema state before tests execute.
\end{itemize}

\subsection*{Tooling Overview}

The following tools are used across all testing levels:

\begin{itemize}
    \item \textbf{JUnit 5} – Test runner for unit and integration tests
    \item \textbf{AssertJ} – Fluent assertion library for readable test output
    \item \textbf{Mockito} – For mocking dependencies during isolated unit testing
    \item \textbf{MockMVC} – For controller-level testing without a real HTTP server
    \item \textbf{TestContainers} – For running real database containers during integration tests
    \item \textbf{Playwright / Selenium} – For system and end-to-end tests via browser simulation
    \item \textbf{Flyway} – For applying database migrations in test environments
\end{itemize}

\subsection*{CI Integration}

\begin{itemize}
    \item Tests are executed via a CI pipeline on each merge request to ensure no regressions.
    \item TestContainers and Flyway enable clean and isolated database states for every CI run.
    \item Test reports are generated and archived to identify failures early.
\end{itemize}

\subsection*{Test Stability and Repeatability}

All tests are designed to be environment-independent. No reliance on shared mutable state or external live systems ensures that results are deterministic and failures are traceable to code changes, not environment noise.

