\hypertarget{section-quality-scenarios}{%
\section{Quality Requirements}\label{section-quality-scenarios}}
\begin{itemize}
    \item \textbf{Functionality}
    \begin{itemize}
        \item The system must allow instructors to log in and manage escape rooms.
        \item Students must be able to join escape rooms easily and interact with all functional elements.
        \item Code editor must provide basic syntax highlighting.
        \item Leaderboards must display real-time progress and timestamps for riddles solved.
    \end{itemize}

    \item \textbf{Performance}
    \begin{itemize}
        \item The system must handle 200 concurrent users in a single escape room without degradation.
        \item Code execution must return results within 10 seconds.
    \end{itemize}

    \item \textbf{Usability}
    \begin{itemize}
        \item Students should be able to join an open escape room within one minute.
        \item Clear positioning of hints and interactive elements across standard screen resolutions.
    \end{itemize}

    \item \textbf{Reliability}
    \begin{itemize}
        \item Progress must persist even after browser cache clearing (server-side tracking).
        \item Resilience to malicious code submissions without system crashes.
        \item The system must gracefully handle partial service outages, ensuring key functionalities remain available.
    \end{itemize}

    \item \textbf{Security}
    \begin{itemize}
        \item Authentication mechanisms must prevent unauthorized access.
        \item User-submitted code must execute in a secure, isolated environment.
        \item All data transmission must use secure protocols (e.g., HTTPS).
    \end{itemize}

    \item \textbf{Data Integrity}
    \begin{itemize}
        \item Escape room results and leaderboard data must be treated as critical and securely stored.
        \item Regular backups must ensure recovery of data in case of corruption or loss.
    \end{itemize}

    \item \textbf{Accessibility}
    \begin{itemize}
        \item The system must comply with WCAG 2.1 standards, with a particular focus on supporting users with red-green color blindness by ensuring appropriate contrast and alternative color cues for critical elements.
\end{itemize}


\hypertarget{_quality_tree}{%
\subsection{Quality Tree}\label{_quality_tree}}
The following quality tree visualizes the main quality goals and their associated sub-goals:
\begin{itemize}
    \item \textbf{Functionality}
    \begin{itemize}
        \item Login for instructors
        \item Interactive escape rooms
        \item Real-time leaderboard updates
    \end{itemize}
    
    \item \textbf{Performance}
    \begin{itemize}
        \item High concurrency
        \item Fast code execution
    \end{itemize}

    \item \textbf{Usability}
    \begin{itemize}
        \item Easy room joining
        \item Clear UI positioning
    \end{itemize}
    
    \item \textbf{Reliability}
    \begin{itemize}
        \item Persistent session progress
        \item Resilience to malicious inputs
        \item Service continuity during partial outages
    \end{itemize}
    
    \item \textbf{Security}
    \begin{itemize}
        \item Role-based access control
        \item Isolated code execution
        \item Secure data transmission
    \end{itemize}
    
    \item \textbf{Data Integrity}
    \begin{itemize}
        \item Secure storage of results
        \item Regular backups
    \end{itemize}
    
    \item \textbf{Accessibility}
    \begin{itemize}
        \item WCAG 2.1 compliance
    \end{itemize}
\end{itemize}

\hypertarget{_quality_scenarios}{%
\subsection{Quality Scenarios}\label{_quality_scenarios}}

\subsection{Functionality Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: Instructor Login}  
    Instructors can log in using secure credentials to open and manage escape rooms.
    \item \textbf{Scenario 2: Real-Time Leaderboard Updates}  
    Leaderboards update instantly after a student completes a riddle.
\end{itemize}

\subsection{Performance Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: High Concurrency}  
    The system handles 200 users interacting simultaneously in a single escape room session.
    \item \textbf{Scenario 2: Fast Code Execution}  
    User-submitted code is executed, and results are returned within 10 seconds.
\end{itemize}

\subsection{Reliability Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: Persistent Progress}  
    If the browser cache is cleared, students can resume from their last completed stage upon re-login.
    \item \textbf{Scenario 2: Malicious Code Handling}  
    The system detects and isolates malicious code submissions without impacting other users.
    \item \textbf{Scenario 3: Service Continuity During Outage}  
    If a microservice fails, the system maintains basic functionality (e.g., leaderboard updates, session progress).
\end{itemize}

\subsection{Security Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: Authentication Failure}  
    If login fails, unauthorized users cannot access restricted features.
    \item \textbf{Scenario 2: Secure Code Execution}  
    Code submissions are run in a sandbox to prevent unauthorized access to system resources.
    \item \textbf{Scenario 3: Data Transmission Security}  
    All communication between client and server uses HTTPS to prevent data interception.
\end{itemize}

\subsection{Data Integrity Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: Leaderboard Data Recovery}  
    After a system crash, all leaderboard data is restored to the last successful save.
    \item \textbf{Scenario 2: Backup Recovery}  
    In the event of data corruption, backup data is restored within 10 minutes.
\end{itemize}

\subsection{Usability Scenarios}
\begin{itemize}
    \item \textbf{Scenario 1: Fast Room Joining}  
    Students can join an open escape room within one minute, even during peak usage.
    \item \textbf{Scenario 2: Hint Accessibility}  
    Hints are visible and accessible on devices with varying screen sizes.
    \item \textbf{Scenario 3: Keyboard Navigation}  
    All key interactions can be completed using a keyboard to ensure accessibility.
\end{itemize}