\hypertarget{section-glossary}{%
\section{Glossary}\label{section-glossary}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.6667}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Definition
\end{minipage} \\
\midrule
\endhead
\emph{\textless Open an escape room\textgreater{}} &
\emph{\textless selecting a escape room and create a playable instance of it. This means the escape room is in the lobby state and join able for students\textgreater{}} \\

\emph{\textless Start an escape room\textgreater{}} &
\emph{\textless Move an escape room from the lobby state into a playing one to enable a synchrony start for all participants \textgreater{}} \\

\emph{\textless Stop an escape room\textgreater{}} &
\emph{\textless Disable the currently running escape room and therefore stop progress for students.\textgreater{}} \\

\emph{\textless Finished an escape room\textgreater{}} &
\emph{\textless The main focus between stopped and finished is that stopped indicates a premature end of the ER, while finished indicates a completed ER session by the defined time-limit. This is used to identify whatever to include an ER in statistics or not. \textgreater{}} \\

\emph{\textless IDE (Integrated Development Environment)\textgreater{}} & 
\emph{\textless A software application that provides comprehensive facilities to programmers for software development, including a code editor, debugger, and build automation tools. \textgreater{}} \\

\emph{\textless Riddle\textgreater{}} & 
\emph{\textless A problem that requires solving by the students in order to solve a level in the escape room \textgreater{}} \\

\emph{\textless Lobby\textgreater{}} & 
\emph{\textless The group of users gathered to participate in an escape room together. \textgreater{}} \\

\emph{\textless Java Spring Boot MVC\textgreater{}} & 
\emph{\textless A framework for building web applications using the Model-View-Controller (MVC) design pattern, streamlining the development of Java-based backends. \textgreater{}} \\

\emph{\textless API (Application Programming Interface)\textgreater{}} & 
\emph{\textless A set of defined methods and protocols that allow different software applications to communicate and exchange data. \textgreater{}} \\

\emph{\textless CI/CD (Continuous Integration and Continuous Deployment)\textgreater{}} & 
\emph{\textless Practices in software development that ensure automated building, testing, and deployment of applications to deliver updates reliably and frequently. \textgreater{}} \\

\emph{\textless GitHub\textgreater{}} & 
\emph{\textless A platform for hosting and collaborating on code repositories using Git version control. \textgreater{}} \\

\emph{\textless Kubernetes\textgreater{}} & 
\emph{\textless An open-source container orchestration platform that automates the deployment, scaling, and management of containerized applications. \textgreater{}} \\

\emph{\textless Kafka\textgreater{}} & 
\emph{\textless An open-source distributed event streaming platform designed for high-throughput and fault-tolerant processing of data streams. \textgreater{}} \\

\emph{\textless RabbitMQ\textgreater{}} & 
\emph{\textless A lightweight, open-source message broker for handling message queuing and ensuring communication between distributed systems. \textgreater{}} \\

\emph{\textless UI (User Interface)\textgreater{}} & 
\emph{\textless The visual and interactive part of an application that users interact with to perform tasks. \textgreater{}} \\

\emph{\textless Fluentd\textgreater{}} & 
\emph{\textless An open-source data collector that unifies the data collection and consumption process across various systems. \textgreater{}} \\

\emph{\textless Pod\textgreater{}} & 
\emph{\textless The smallest deployable unit in Kubernetes, representing a group of containers that share the same network and storage. \textgreater{}} \\

\emph{\textless Keycloak\textgreater{}} & 
\emph{\textless An external identity and access management service providing OAuth-based authentication and token issuance. \textgreater{}} \\

\emph{\textless OAuth (Open Authorization)\textgreater{}} & 
\emph{\textless An open standard for access delegation, allowing users to grant applications limited access to their resources without exposing credentials. \textgreater{}} \\

\emph{\textless Prometheus\textgreater{}} & 
\emph{\textless A monitoring tool that collects metrics from services and stores them in a time-series database for querying and alerting. \textgreater{}} \\

\emph{\textless Grafana\textgreater{}} & 
\emph{\textless A visualization tool used to query and display metrics from Prometheus and other data sources, often used for creating centralized dashboards. \textgreater{}} \\

\emph{\textless ADR (Architecture Decision Record)\textgreater{}} & 
\emph{\textless A document capturing an important architectural decision made along with its context and rationale. \textgreater{}} \\

\emph{\textless HTTPS (Hypertext Transfer Protocol Secure)\textgreater{}} & 
\emph{\textless A secure version of HTTP that encrypts data between the browser and server using SSL/TLS protocols. \textgreater{}} \\

\emph{\textless WCAG 2.1 (Web Content Accessibility Guidelines)\textgreater{}} & 
\emph{\textless A standard outlining best practices for making web content accessible to people with disabilities. \textgreater{}} \\


\bottomrule
\end{longtable}